---
title: "Preprocessing Script"
author: "Sofie Ditmer"
date: "9/22/2020"
output: html_document
---

This script provides you with a pipeline for preprocessing one data file of the Danish Gigaword Corpus (Strømberg-Derczynski et al., 2020). The preprocessing includes standard natural language processing steps such as tokenization and lemmatization. 
Hence, this script is provided to demonstrate what has been done with the entire Danish Gigaword Corpus demonstrated on a single text-file. Running this script will provide you with a preprocessed csv-file of pure text.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r}
library(pacman)
pacman::p_load(readtext, tidyverse, pastecs, WRS2, tidyselect, brms, rethinking, bayesplot, udpipe, stopwords, textclean)
```

# Load data
```{r}
data <- read.delim("/Users/jdi/CulturalDataScienceExamProject2020/Subset_DAGW/folketinget.txt", header=FALSE, quote="", fill=FALSE) 
```

# Load UDpipe Danish Model
```{r}
# Get danish model
danish <- udpipe_download_model(language = "danish")
str(danish)

# Load danish model
udmodel_danish  <- udpipe_load_model(file = "danish-ddt-ud-2.4-190531.udpipe")
```

Make text into lowercase, remove punctuation, and remove numbers
```{r}
data[,1] <- tolower(data[,1]) # make it lowercase
data[,1] <- gsub("[[:punct:]]", "", data[,1]) # remove punctuation
data[,1] <- gsub("[[:digit:]]", "", data[,1]) # remove numbers
```

Remove stopwords
```{r}
# Using the stopwords package to get the list of Danish stopwords
list_of_stopwords <- stopwords::stopwords("da", source = "snowball")

# Remove stopwords
stopwords_regex = paste(stopwords('da'), collapse = '\\b|\\b')
stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
data[,1] <- stringr::str_replace_all(data[,1], stopwords_regex, '')
```

Tokenization, tagging, lemmatization, and dependency parsing
```{r}
x <- udpipe_annotate(udmodel_danish, x = data[,1])
x <- as.data.frame(x)
str(x)
table(x$upos)
```

Create the right format for gensim module Word2vec function in Python
```{r}
# Make a copy of the data first
x2 <- x

# Remove "doc" so we only have numbers
x2$doc_id <- stringr::str_replace_all(x2$doc_id, "doc", "")
x2$doc_id <- as.numeric(x2$doc_id)

# Collapse
x2 <- x2 %>%
  select(doc_id, lemma) %>% 
  group_by(doc_id) %>% 
  summarize(sentence = str_c(lemma, collapse = ", ")) %>% 
  arrange()

# Remove doc_id column
x2$doc_id <- NULL

# Remove commas
x2$sentence <- gsub("[[:punct:]]", "", x2$sentence)
```

Making a csv-file
```{r}
write.csv(x2, file = "preprocessed_data.csv", row.names = FALSE, col.names = NA)
```













